---
title: "DSMB Report for *Project Name*"
output: 
  html_document:
    number_sections: true
---



# *DSMB Plan*

*Preparation Date*: `r Sys.Date()`


# *Design Summary*

## Study Abstract

## Primary Hypothesis

## Primary and Secondary Aims

## Inclusion and Exclusion Criteria

## Intervention Group

## Primary and Secondary Outcomes

## Target Sample Size and Allocation

## Data Collection Schedule

## Timeline

# Overall Study Status - Narrative

## DSMB Meeting Minutes

## Action Items and Response

## Study Status and Chronolog since Previous Meeting

## Challenges since Last Report and Steps to Handle Them

# Recruitment and Participant Status

*Insert figure with participant flow chart*

```{r, echo = FALSE}

grViz(readd(consort_dot))

```

```{r, echo = FALSE}

kable(readd(consort_table))

```


# Enrollment and Randomization

## Current Enrollment and Randomization Numbers
*Insert figure with randomization actual vs expected*


*Insert table with screening, enrollment, randomization and withdrawal numbers*


*Insert table with counts of reasons for ineligibility among the consented*

## Barriers to Meeting Recruitment Goals

## Strategies in Place or Planned to Address Recruitment Shortfalls

# Baseline Characteristics

*Insert table with demographic summary statistics of randomized participants*

# Study Withdrawal

*Table with counts of reasons for study withdrawal*

*Table with date, time point and details for individal withdrawals*

# Study Visit Completion and Data Recorded

*insert graph showing missing visits*

*insert table of visit completion status by site*

# Protocol Deviations

*insert table of protocol deviations*

# Safety Data

## Serious Adverse Events

*insert table of serious adverse events by body system*

*insert table of serious adverse event descriptions*

## Non-Serious Adverse Events

*insert table of non-serious adverse events by body system*

## Unanticipated Problems

*insert table of unanticipated problems*

# Any Other Pertinent Issues

















